### 2020-10-05 rR.tex
so close

% Created by tikzDevice version 0.12.3 on 2020-04-29 03:55:17
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,433.62);
\begin{scope}
\path[clip] (  0.00,216.81) rectangle (289.08,433.62);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,216.81) rectangle (289.08,433.62);
\end{scope}
\begin{scope}
\path[clip] ( 27.31,247.50) rectangle (283.58,410.96);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.31,247.50) rectangle (283.58,410.96);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.94,254.97) --
	( 55.54,255.77) --
	( 58.13,256.58) --
	( 60.73,257.40) --
	( 63.32,258.23) --
	( 65.92,259.08) --
	( 68.51,259.94) --
	( 71.11,260.81) --
	( 73.70,261.69) --
	( 76.30,262.59) --
	( 78.89,263.49) --
	( 81.49,264.42) --
	( 84.08,265.35) --
	( 86.68,266.30) --
	( 89.27,267.26) --
	( 91.87,268.23) --
	( 94.46,269.21) --
	( 97.06,270.20) --
	( 99.65,271.21) --
	(102.25,272.23) --
	(104.84,273.26) --
	(107.44,274.30) --
	(110.03,275.36) --
	(112.63,276.43) --
	(115.22,277.51) --
	(117.82,278.61) --
	(120.41,279.72) --
	(123.01,280.84) --
	(125.60,281.98) --
	(128.20,283.13) --
	(130.79,284.29) --
	(133.39,285.46) --
	(135.98,286.65) --
	(138.58,287.85) --
	(141.17,289.07) --
	(143.77,290.31) --
	(146.36,291.55) --
	(148.96,292.82) --
	(151.55,294.10) --
	(154.15,295.40) --
	(156.74,296.71) --
	(159.34,298.04) --
	(161.93,299.39) --
	(164.53,300.75) --
	(167.12,302.12) --
	(169.72,303.51) --
	(172.31,304.92) --
	(174.91,306.34) --
	(177.51,307.78) --
	(180.10,309.24) --
	(182.70,310.71) --
	(185.29,312.21) --
	(187.89,313.72) --
	(190.48,315.26) --
	(193.08,316.81) --
	(195.67,318.38) --
	(198.27,319.97) --
	(200.86,321.57) --
	(203.46,323.20) --
	(206.05,324.84) --
	(208.65,326.51) --
	(211.24,328.19) --
	(213.84,329.89) --
	(216.43,331.62) --
	(219.03,333.36) --
	(221.62,335.12) --
	(224.22,336.91) --
	(226.81,338.72) --
	(229.41,340.54) --
	(232.00,342.39) --
	(234.60,344.25) --
	(237.19,346.14) --
	(239.79,348.04) --
	(242.38,349.97) --
	(244.98,351.91) --
	(247.57,353.87) --
	(250.17,355.85) --
	(252.76,357.85) --
	(255.36,359.88) --
	(257.95,361.92);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.52) --
	( 30.34,248.34) --
	( 33.37,249.16) --
	( 36.40,250.01) --
	( 39.42,250.87) --
	( 42.45,251.74) --
	( 45.48,252.64) --
	( 48.51,253.54) --
	( 51.53,254.47) --
	( 54.56,255.41) --
	( 57.59,256.36) --
	( 60.62,257.34) --
	( 63.64,258.32) --
	( 66.67,259.33) --
	( 69.70,260.35) --
	( 72.73,261.38) --
	( 75.76,262.43) --
	( 78.78,263.50) --
	( 81.81,264.58) --
	( 84.84,265.68) --
	( 87.87,266.80) --
	( 90.89,267.93) --
	( 93.92,269.08) --
	( 96.95,270.25) --
	( 99.98,271.42) --
	(103.00,272.61) --
	(106.03,273.81) --
	(109.06,275.03) --
	(112.09,276.26) --
	(115.11,277.51) --
	(118.14,278.77) --
	(121.17,280.06) --
	(124.20,281.37) --
	(127.22,282.71) --
	(130.25,284.06) --
	(133.28,285.44) --
	(136.31,286.83) --
	(139.34,288.23) --
	(142.36,289.64) --
	(145.39,291.08) --
	(148.42,292.53) --
	(151.45,294.01) --
	(154.47,295.51) --
	(157.50,297.03) --
	(160.53,298.59) --
	(163.56,300.17) --
	(166.58,301.77) --
	(169.61,303.39) --
	(172.64,305.02) --
	(175.67,306.68) --
	(178.69,308.35) --
	(181.72,310.04) --
	(184.75,311.76) --
	(187.78,313.51) --
	(190.80,315.28) --
	(193.83,317.09) --
	(196.86,318.92) --
	(199.89,320.80) --
	(202.92,322.69) --
	(205.94,324.62) --
	(208.97,326.56) --
	(212.00,328.54) --
	(215.03,330.54) --
	(218.05,332.56) --
	(221.08,334.62) --
	(224.11,336.70) --
	(227.14,338.80) --
	(230.16,340.94) --
	(233.19,343.10) --
	(236.22,345.29) --
	(239.25,347.50) --
	(242.27,349.75) --
	(245.30,352.02) --
	(248.33,354.31) --
	(251.36,356.63) --
	(254.39,358.98) --
	(257.41,361.36) --
	(260.44,363.76) --
	(263.47,366.19) --
	(266.50,368.65);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.91) --
	( 38.88,250.76) --
	( 41.91,251.62) --
	( 44.94,252.51) --
	( 47.97,253.41) --
	( 50.99,254.32) --
	( 54.02,255.26) --
	( 57.05,256.21) --
	( 60.08,257.17) --
	( 63.10,258.15) --
	( 66.13,259.15) --
	( 69.16,260.17) --
	( 72.19,261.20) --
	( 75.21,262.25) --
	( 78.24,263.31) --
	( 81.27,264.39) --
	( 84.30,265.48) --
	( 87.33,266.60) --
	( 90.35,267.72) --
	( 93.38,268.87) --
	( 96.41,270.03) --
	( 99.44,271.21) --
	(102.46,272.41) --
	(105.49,273.62) --
	(108.52,274.84) --
	(111.55,276.08) --
	(114.57,277.32) --
	(117.60,278.59) --
	(120.63,279.86) --
	(123.66,281.16) --
	(126.68,282.48) --
	(129.71,283.81) --
	(132.74,285.17) --
	(135.77,286.56) --
	(138.79,287.97) --
	(141.82,289.39) --
	(144.85,290.83) --
	(147.88,292.29) --
	(150.91,293.76) --
	(153.93,295.24) --
	(156.96,296.75) --
	(159.99,298.28) --
	(163.02,299.84) --
	(166.04,301.42) --
	(169.07,303.03) --
	(172.10,304.67) --
	(175.13,306.33) --
	(178.15,308.01) --
	(181.18,309.70) --
	(184.21,311.42) --
	(187.24,313.15) --
	(190.26,314.90) --
	(193.29,316.68) --
	(196.32,318.49) --
	(199.35,320.33) --
	(202.37,322.21) --
	(205.40,324.12) --
	(208.43,326.06) --
	(211.46,328.03) --
	(214.49,330.03) --
	(217.51,332.06) --
	(220.54,334.11) --
	(223.57,336.19) --
	(226.60,338.30) --
	(229.62,340.44) --
	(232.65,342.61) --
	(235.68,344.80) --
	(238.71,347.02) --
	(241.73,349.28) --
	(244.76,351.56) --
	(247.79,353.87) --
	(250.82,356.21) --
	(253.84,358.58) --
	(256.87,360.97) --
	(259.90,363.40) --
	(262.93,365.85) --
	(265.95,368.33) --
	(268.98,370.84) --
	(272.01,373.38) --
	(275.04,375.95);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.39) --
	( 47.43,253.28) --
	( 50.45,254.18) --
	( 53.48,255.11) --
	( 56.51,256.05) --
	( 59.54,257.00) --
	( 62.56,257.98) --
	( 65.59,258.97) --
	( 68.62,259.97) --
	( 71.65,261.00) --
	( 74.67,262.04) --
	( 77.70,263.10) --
	( 80.73,264.17) --
	( 83.76,265.26) --
	( 86.78,266.37) --
	( 89.81,267.49) --
	( 92.84,268.63) --
	( 95.87,269.79) --
	( 98.89,270.97) --
	(101.92,272.16) --
	(104.95,273.37) --
	(107.98,274.60) --
	(111.01,275.84) --
	(114.03,277.11) --
	(117.06,278.38) --
	(120.09,279.67) --
	(123.12,280.97) --
	(126.14,282.28) --
	(129.17,283.61) --
	(132.20,284.96) --
	(135.23,286.33) --
	(138.25,287.72) --
	(141.28,289.14) --
	(144.31,290.58) --
	(147.34,292.05) --
	(150.36,293.53) --
	(153.39,295.03) --
	(156.42,296.54) --
	(159.45,298.06) --
	(162.48,299.61) --
	(165.50,301.18) --
	(168.53,302.77) --
	(171.56,304.38) --
	(174.59,306.03) --
	(177.61,307.70) --
	(180.64,309.41) --
	(183.67,311.14) --
	(186.70,312.89) --
	(189.72,314.66) --
	(192.75,316.45) --
	(195.78,318.25) --
	(198.81,320.09) --
	(201.83,321.94) --
	(204.86,323.83) --
	(207.89,325.76) --
	(210.92,327.71) --
	(213.94,329.71) --
	(216.97,331.74) --
	(220.00,333.80) --
	(223.03,335.89) --
	(226.06,338.01) --
	(229.08,340.16) --
	(232.11,342.33) --
	(235.14,344.54) --
	(238.17,346.77) --
	(241.19,349.04) --
	(244.22,351.34) --
	(247.25,353.67) --
	(250.28,356.02) --
	(253.30,358.41) --
	(256.33,360.83) --
	(259.36,363.28) --
	(262.39,365.76) --
	(265.41,368.27) --
	(268.44,370.81) --
	(271.47,373.38) --
	(274.50,375.98) --
	(277.52,378.61) --
	(280.55,381.26) --
	(283.58,383.95);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 27.31,251.38) --
	( 30.68,245.55) --
	( 23.95,245.55) --
	cycle;

\path[fill=fillColor] ( 61.48,261.57) --
	( 64.85,255.75) --
	( 58.12,255.75) --
	cycle;

\path[fill=fillColor] ( 95.65,273.63) --
	( 99.01,267.80) --
	( 92.29,267.80) --
	cycle;

\path[fill=fillColor] (129.82,287.78) --
	(133.18,281.95) --
	(126.46,281.95) --
	cycle;

\path[fill=fillColor] (163.99,304.26) --
	(167.35,298.43) --
	(160.63,298.43) --
	cycle;

\path[fill=fillColor] (198.16,323.63) --
	(201.52,317.81) --
	(194.79,317.81) --
	cycle;

\path[fill=fillColor] (232.33,346.20) --
	(235.69,340.37) --
	(228.96,340.37) --
	cycle;

\path[fill=fillColor] (266.50,372.59) --
	(269.86,366.77) --
	(263.13,366.77) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 33.36,247.39) --
	( 38.35,247.39) --
	( 38.35,252.38) --
	( 33.36,252.38) --
	cycle;

\path[fill=fillColor] ( 67.53,258.02) --
	( 72.52,258.02) --
	( 72.52,263.01) --
	( 67.53,263.01) --
	cycle;

\path[fill=fillColor] (101.70,270.61) --
	(106.69,270.61) --
	(106.69,275.61) --
	(101.70,275.61) --
	cycle;

\path[fill=fillColor] (135.86,285.30) --
	(140.86,285.30) --
	(140.86,290.30) --
	(135.86,290.30) --
	cycle;

\path[fill=fillColor] (170.03,302.36) --
	(175.03,302.36) --
	(175.03,307.36) --
	(170.03,307.36) --
	cycle;

\path[fill=fillColor] (204.20,322.52) --
	(209.20,322.52) --
	(209.20,327.51) --
	(204.20,327.51) --
	cycle;

\path[fill=fillColor] (238.37,345.90) --
	(243.37,345.90) --
	(243.37,350.89) --
	(238.37,350.89) --
	cycle;

\path[fill=fillColor] (272.54,373.53) --
	(277.54,373.53) --
	(277.54,378.53) --
	(272.54,378.53) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,252.37) -- ( 47.93,252.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.83) -- ( 44.40,255.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.46) -- ( 82.10,263.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.93) -- ( 78.57,266.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.06) -- (112.74,280.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.31) -- (146.90,295.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.13) -- (181.07,313.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.17) -- (252.94,355.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.64) -- (249.41,358.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,384.02) -- (287.11,384.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.49) -- (283.58,387.55);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 52.94,254.96) circle (  2.50);

\path[fill=fillColor] ( 87.11,266.50) circle (  2.50);

\path[fill=fillColor] (121.28,280.09) circle (  2.50);

\path[fill=fillColor] (155.45,296.05) circle (  2.50);

\path[fill=fillColor] (189.62,314.74) circle (  2.50);

\path[fill=fillColor] (223.78,336.55) circle (  2.50);

\path[fill=fillColor] (257.95,361.93) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 27.31,247.50) rectangle (283.58,410.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,387.61) --
	( 27.31,387.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-10-04 14:51:35
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,433.62);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,387.61) --
	( 27.31,387.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Basic reproduction number $\mathcal R_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,244.47) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,291.17) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,337.88) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,384.58) {4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,247.50) --
	(319.81,247.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,294.20) --
	(319.81,294.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,340.91) --
	(319.81,340.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,387.61) --
	(319.81,387.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (305.58,329.23) {Reproduction number ${\mathcal R}_{\textrm{\tiny intrinsic}}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36, 60.52) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 22.36,170.08) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56, 63.55) --
	( 27.31, 63.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.56,173.11) --
	( 27.31,173.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.42) {Mean interval (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86, 27.66) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86, 66.58) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,105.50) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,144.42) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.86,183.34) {0.8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06, 30.69) --
	(319.81, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06, 69.61) --
	(319.81, 69.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,108.53) --
	(319.81,108.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,147.45) --
	(319.81,147.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (317.06,186.37) --
	(319.81,186.37);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (298.73,112.42) {Squared coefficient of variation};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,419.03) {A};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (319.81,419.03) {B};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 27.31,202.22) {C};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (319.81,202.22) {D};
\end{scope}
\begin{scope}
\path[clip] ( 27.31,247.50) rectangle (280.16,410.96);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.31,247.50) rectangle (280.16,410.96);
\definecolor{drawColor}{RGB}{13,8,135}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.50) --
	( 29.98,248.23) --
	( 32.65,248.97) --
	( 35.31,249.73) --
	( 37.98,250.50) --
	( 40.65,251.28) --
	( 43.32,252.08) --
	( 45.98,252.88) --
	( 48.65,253.70) --
	( 51.32,254.53) --
	( 53.98,255.37) --
	( 56.65,256.23) --
	( 59.32,257.09) --
	( 61.99,257.97) --
	( 64.65,258.86) --
	( 67.32,259.76) --
	( 69.99,260.67) --
	( 72.65,261.60) --
	( 75.32,262.53) --
	( 77.99,263.48) --
	( 80.66,264.43) --
	( 83.32,265.40) --
	( 85.99,266.38) --
	( 88.66,267.37) --
	( 91.32,268.38) --
	( 93.99,269.40) --
	( 96.66,270.43) --
	( 99.33,271.47) --
	(101.99,272.54) --
	(104.66,273.61) --
	(107.33,274.70) --
	(109.99,275.81) --
	(112.66,276.93) --
	(115.33,278.07) --
	(118.00,279.22) --
	(120.66,280.38) --
	(123.33,281.55) --
	(126.00,282.74) --
	(128.66,283.95) --
	(131.33,285.16) --
	(134.00,286.40) --
	(136.67,287.65) --
	(139.33,288.91) --
	(142.00,290.20) --
	(144.67,291.50) --
	(147.33,292.81) --
	(150.00,294.15) --
	(152.67,295.51) --
	(155.34,296.88) --
	(158.00,298.27) --
	(160.67,299.67) --
	(163.34,301.09) --
	(166.00,302.53) --
	(168.67,303.98) --
	(171.34,305.45) --
	(174.01,306.94) --
	(176.67,308.45) --
	(179.34,309.97) --
	(182.01,311.51) --
	(184.67,313.08) --
	(187.34,314.67) --
	(190.01,316.27) --
	(192.68,317.90) --
	(195.34,319.55) --
	(198.01,321.23) --
	(200.68,322.92) --
	(203.34,324.64) --
	(206.01,326.37) --
	(208.68,328.13) --
	(211.35,329.90) --
	(214.01,331.70) --
	(216.68,333.51) --
	(219.35,335.35) --
	(222.01,337.21) --
	(224.68,339.08) --
	(227.35,340.98) --
	(230.02,342.90) --
	(232.68,344.83) --
	(235.35,346.79) --
	(238.02,348.77);
\definecolor{drawColor}{RGB}{126,3,168}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 61.03,257.69) --
	( 63.69,258.56) --
	( 66.36,259.45) --
	( 69.03,260.35) --
	( 71.69,261.26) --
	( 74.36,262.19) --
	( 77.03,263.13) --
	( 79.70,264.08) --
	( 82.36,265.05) --
	( 85.03,266.03) --
	( 87.70,267.03) --
	( 90.36,268.04) --
	( 93.03,269.06) --
	( 95.70,270.09) --
	( 98.37,271.14) --
	(101.03,272.21) --
	(103.70,273.28) --
	(106.37,274.37) --
	(109.03,275.47) --
	(111.70,276.58) --
	(114.37,277.71) --
	(117.04,278.84) --
	(119.70,279.99) --
	(122.37,281.16) --
	(125.04,282.34) --
	(127.70,283.53) --
	(130.37,284.74) --
	(133.04,285.97) --
	(135.71,287.21) --
	(138.37,288.47) --
	(141.04,289.75) --
	(143.71,291.04) --
	(146.37,292.36) --
	(149.04,293.69) --
	(151.71,295.03) --
	(154.38,296.39) --
	(157.04,297.76) --
	(159.71,299.15) --
	(162.38,300.55) --
	(165.04,301.97) --
	(167.71,303.41) --
	(170.38,304.87) --
	(173.05,306.34) --
	(175.71,307.84) --
	(178.38,309.35) --
	(181.05,310.89) --
	(183.71,312.45) --
	(186.38,314.03) --
	(189.05,315.62) --
	(191.72,317.24) --
	(194.38,318.87) --
	(197.05,320.53) --
	(199.72,322.19) --
	(202.38,323.88) --
	(205.05,325.59) --
	(207.72,327.32) --
	(210.39,329.07) --
	(213.05,330.84) --
	(215.72,332.63) --
	(218.39,334.45) --
	(221.05,336.29) --
	(223.72,338.15) --
	(226.39,340.04) --
	(229.06,341.96) --
	(231.72,343.90) --
	(234.39,345.87) --
	(237.06,347.86) --
	(239.72,349.87) --
	(242.39,351.90) --
	(245.06,353.96) --
	(247.73,356.04) --
	(250.39,358.15) --
	(253.06,360.28) --
	(255.73,362.43) --
	(258.39,364.60) --
	(261.06,366.80) --
	(263.73,369.02) --
	(266.40,371.27) --
	(269.06,373.53) --
	(271.73,375.82);
\definecolor{drawColor}{RGB}{204,70,120}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 52.60,254.98) --
	( 55.26,255.81) --
	( 57.93,256.66) --
	( 60.60,257.53) --
	( 63.27,258.41) --
	( 65.93,259.30) --
	( 68.60,260.20) --
	( 71.27,261.12) --
	( 73.93,262.04) --
	( 76.60,262.99) --
	( 79.27,263.94) --
	( 81.94,264.91) --
	( 84.60,265.89) --
	( 87.27,266.89) --
	( 89.94,267.90) --
	( 92.60,268.92) --
	( 95.27,269.95) --
	( 97.94,271.00) --
	(100.61,272.05) --
	(103.27,273.12) --
	(105.94,274.20) --
	(108.61,275.30) --
	(111.27,276.40) --
	(113.94,277.52) --
	(116.61,278.66) --
	(119.28,279.81) --
	(121.94,280.97) --
	(124.61,282.15) --
	(127.28,283.34) --
	(129.94,284.55) --
	(132.61,285.78) --
	(135.28,287.03) --
	(137.95,288.29) --
	(140.61,289.56) --
	(143.28,290.85) --
	(145.95,292.16) --
	(148.62,293.48) --
	(151.28,294.81) --
	(153.95,296.16) --
	(156.62,297.52) --
	(159.28,298.90) --
	(161.95,300.30) --
	(164.62,301.72) --
	(167.29,303.16) --
	(169.95,304.61) --
	(172.62,306.09) --
	(175.29,307.58) --
	(177.95,309.10) --
	(180.62,310.64) --
	(183.29,312.20) --
	(185.96,313.77) --
	(188.62,315.36) --
	(191.29,316.96) --
	(193.96,318.59) --
	(196.62,320.23) --
	(199.29,321.89) --
	(201.96,323.58) --
	(204.63,325.28) --
	(207.29,327.01) --
	(209.96,328.76) --
	(212.63,330.54) --
	(215.29,332.33) --
	(217.96,334.16) --
	(220.63,336.01) --
	(223.30,337.88) --
	(225.96,339.78) --
	(228.63,341.70) --
	(231.30,343.64) --
	(233.96,345.60) --
	(236.63,347.59) --
	(239.30,349.60) --
	(241.97,351.63) --
	(244.63,353.69) --
	(247.30,355.76) --
	(249.97,357.86) --
	(252.63,359.99) --
	(255.30,362.13) --
	(257.97,364.30) --
	(260.64,366.49) --
	(263.30,368.71);
\definecolor{drawColor}{RGB}{248,148,65}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.17,252.37) --
	( 46.84,253.17) --
	( 49.50,253.99) --
	( 52.17,254.82) --
	( 54.84,255.66) --
	( 57.51,256.51) --
	( 60.17,257.37) --
	( 62.84,258.25) --
	( 65.51,259.14) --
	( 68.17,260.05) --
	( 70.84,260.97) --
	( 73.51,261.90) --
	( 76.18,262.84) --
	( 78.84,263.79) --
	( 81.51,264.76) --
	( 84.18,265.74) --
	( 86.84,266.74) --
	( 89.51,267.74) --
	( 92.18,268.76) --
	( 94.85,269.79) --
	( 97.51,270.83) --
	(100.18,271.88) --
	(102.85,272.95) --
	(105.51,274.03) --
	(108.18,275.12) --
	(110.85,276.23) --
	(113.52,277.35) --
	(116.18,278.49) --
	(118.85,279.64) --
	(121.52,280.80) --
	(124.18,281.98) --
	(126.85,283.18) --
	(129.52,284.39) --
	(132.19,285.61) --
	(134.85,286.85) --
	(137.52,288.09) --
	(140.19,289.35) --
	(142.85,290.63) --
	(145.52,291.92) --
	(148.19,293.22) --
	(150.86,294.54) --
	(153.52,295.88) --
	(156.19,297.23) --
	(158.86,298.61) --
	(161.52,300.00) --
	(164.19,301.41) --
	(166.86,302.85) --
	(169.53,304.30) --
	(172.19,305.78) --
	(174.86,307.28) --
	(177.53,308.79) --
	(180.19,310.32) --
	(182.86,311.86) --
	(185.53,313.42) --
	(188.20,315.01) --
	(190.86,316.61) --
	(193.53,318.23) --
	(196.20,319.88) --
	(198.86,321.54) --
	(201.53,323.23) --
	(204.20,324.94) --
	(206.87,326.68) --
	(209.53,328.43) --
	(212.20,330.22) --
	(214.87,332.02) --
	(217.53,333.85) --
	(220.20,335.71) --
	(222.87,337.58) --
	(225.54,339.48) --
	(228.20,341.40) --
	(230.87,343.34) --
	(233.54,345.30) --
	(236.20,347.28) --
	(238.87,349.29) --
	(241.54,351.32) --
	(244.21,353.37) --
	(246.87,355.45) --
	(249.54,357.54) --
	(252.21,359.66) --
	(254.87,361.80);
\definecolor{drawColor}{RGB}{216,224,30}
